Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-06-11 article.tex
typos

\section{Computing the longest $(213,231)$-avoiding subsequence}
\label{section:LCS}

	This section is devoted to finding longest $(213,231)$-avoiding subsequences in permutations:
	Given a set of permutations, find a longest $(213,231)$-avoiding that occurs as a pattern
	in each input permutation.

	We start with the easiest case where we are given just one input permutation.
	We need the set of descent elements and the set of ascent elements.
	$P(\pi) = \{i | \stripe{\pi}{i} = \ustep \} \cup \{n\}$ and
	$M(\pi) = \{i | \stripe{\pi}{i} = \dstep \} \cup \{n\}$.\\

@@

\begin{proof}
Consider the following problem,
that compute the longest stripe common to $\pi_1$ and $\pi_2$.
Given two permutations $\pi_1$ and $\pi_2$.\\

$$
\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
$$
\begin{center}
= $\max$ \{$|s|$ $|$ $s$ occurs in $\pi_1[i_1:]$ with every element is in $[\lb_1,\ub_1]$ and $s$ occurs in $\pi_2[i_2:]$ with every element is in $[\lb_2,\ub_2]$ \}
\end{center}

We show that this family of problems are closed under induction.\\

>>>>

\section{Computing the longest $(213,231)$-avoiding pattern}
\label{section:LCS}

	This section is devoted to finding longest $(213,231)$-avoiding patterns 
	in permutations.
	We start with the easiest case where we are given just one input permutation
	and we are asked to find the longest $(213,231)$-avoiding pattern that 
	occurs in the input permutation.
	We need the set of descent elements and the set of ascent elements.
	$P(\pi) = \{i | \stripe{\pi}{i} = \ustep \} \cup \{n\}$ and
	$M(\pi) = \{i | \stripe{\pi}{i} = \dstep \} \cup \{n\}$.\\

@@

\begin{proof}
Consider the following problem,
that compute the longest stripe common to $\pi_1$ and $\pi_2$:
Given two permutations $\pi_1$ and $\pi_2$, we define
$
\LCS{\pi_1}{\lb_1}{\ub_1}{\pi_2}{\lb_2}{\ub_2}{i_1}{i_2}
=
\max\{|s| \;|\; s \text{ occurs in } \pi_1[i_1:] \text{ with every element is in }
[\lb_1,\ub_1] \text{ and } s \text{ occurs in } \pi_2[i_2:] \text{ with every element is in }
[\lb_2,\ub_2]\}$.

We show that this family of problems is closed under induction.
